### 2023-10-17 doc/Thesis/chapter/04-experimental.tex
corrected until comp details

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimization section the boundaries for the optimization were investigated. 
And during the third and final step the experiments for the optimization were performed.
\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic solution}\label{sec:exp-sol-aq}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous layers. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
Five different concentrations of the buthanolic solutions were prepared. 
The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Most steel substrates (all pre-optimization and optimization samples) 
All steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
%
Eventually, a heatable vacuum plate was used. It 
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep the substrate in place (see 
figure~\ref{fig:eric}). 
Most of them were covered with tape to increase the suction intensity at the remaining ones. 
After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization samples, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (1) on the left,
		vacuum pump (2) in the background and 
		Erichsen Coatmaster 510 film applicator (3) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

to evaporate. 

@@

The glass plate of the film applicator was therefore exchanged with a metal plate which 

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability. 
Therefore \gls{ipo} was used  as stabilization in further experiments.
After the boundaries of the solution were fixed 
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals, substrates, experimental procedures and any used
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
\td{The experiments can be split into three sections: }
In the first section the base recipe and the base process were sought. 
In the pre-optimization section the boundaries for the optimization were investigated. 
And during the third and final step the experiments for the optimization were performed.
\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic solution}\label{sec:exp-sol-aq}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous layers. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
Five different concentrations of the buthanolic solutions were prepared. 
Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
but higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape to increase the suction intensity at the remaining ones (see figure~\ref{fig:eric}
After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

to evaporate at room temperature. 

@@

The \td{glass plate of the film applicator was therefore exchanged with a metal plate which}

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability of the solution. 
Therefore \gls{ipo} was used  as stabilzier in further experiments.
\td{After the boundaries of the solution were fixed }
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
\td{See} table \ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi
